\clearpage
\phantomsection				
\addcontentsline{toc}{chapter}{\bibname}	% Добавляем список литературы в оглавление
\bibliography{biblio}	

\begin{itemize}
\item[1.] Von Luxburg U., Radl A., Hein M. Hitting and commute times in large random neighborhood graphs //The Journal of Machine Learning Research. – 2014. – Т. 15. – №. 1. – С. 1751-1798.


\item[1.] P. Chebotarev. Studying new classes of graph metrics // F. Nielsen and F. Barbaresco (Eds.), Proceedings of the SEE Conference “Geometric Science of Information” (GSI 2013). Lecture Notes in Computer Science, LNCS 8085. Springer, Berlin, 2013. P. 207–214.

\item[2.] Chebotarev P. Y., Shamis E. V. On a Duality between Metrics and $\ Sigma $-Proximities //arXiv preprint math/0508183. – 2005.

\item[2.] Hitting and Commute Times in Large Random Neighborhood Graphs, U. von Luxburg, A. Radl, M. Hein.
//Journal of Machine Learning Research 15 (2014) 1751-1798

\item[3.] A class of graph-geodetic distances generalizing the shortest-path and the resistance distances, P. Chebotarev. 
//Discrete Applied Mathematics 159 (2011) 295–302

\item[4.] Shortest path distance in random k-nearest neighbor graphs, M. Alamgir, U. von Luxburg (2012)

\item[5.] P.Chebotarev, E.Shamis. The forest metrics for graph vertices // Electronic Notes in Discrete Mathematics. 2002. V.11. P. 98–107.

\item[6.] E. Estrada. The communicability distance in graphs // Linear Algebra and its Applications. 2012. V. 436. P. 4317–4328.

\item[7.] I.Kivimäki, M. Shimbo, M. Saerens. Developments in the theory of randomized shortest paths with a comparison of graph node distances // Physica A: Statistical Mechanics and its Applications. 2014. V. 393. P. 600–616.
 
\item[8.] R.W. Floyd. Algorithm 97: Shortest path. //Communication of the ACM 5(6):345, 1962.

\item[9.] K. Avranchenkov, A. Mishenin, P. Gonçalves, M. Sokol. Generalized Optimization Framework for Graph-based Semi-supervised Learning // In: Proceedings of SIAM Conference on Data Mining (SDM 2012)

\item[10.] Chebotarev Walk distances in graphs

\item[11.] Chebotarev. The forest metric for graph vertices.

\end{itemize}